\documentclass[letterpaper,10pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

% Font options
\usepackage[sfdefault]{roboto}  % Sans-serif font

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Section formatting
\titleformat{\section}{\Large\bfseries\scshape\raggedright}{}{0em}{}[\titlerule]

% Ensure PDF is machine readable
\pdfgentounicode=1

% Custom commands
\newcommand{\resumeItem}[1]{\item\small{#1}}
\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}
  \item \textbf{#1, #2 $|$ #3 $|$ #4}
}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}
\newcommand{\resumeSubHeadingList}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}

\begin{document}

\begin{center}
  \textbf{\Huge William Glazer-Cavanagh} \\
\end{center}

% 1. PROFESSIONAL SUMMARY
\section*{Applied ML Engineer $|$ Bridging Research \& Production}
% value proposition and example, personnal pizzaz
I'm a Software Engineer / ML Scientist bridging the gap between research and production systems.
I can deconstruct State-of-the-Art papers, profile GPU bottlenecks, iterate on experimental hypotheses, and translate technical complexity into plain English.

% 2. CONTACT INFORMATION
\section{Contact Information}
\vspace{-6pt}
\begin{itemize}[leftmargin=0.15in, label={}, itemsep=-3pt]
  \resumeItem{
    \textbf{Phone}: 438-389-8650
    $|$ \textbf{Email}: \href{mailto:willcavanagh@hotmail.com}{willcavanagh@hotmail.com}
    $|$ \textbf{Location}: Montreal, QC / Vancouver, BC
    \\
    \textbf{LinkedIn}: \href{https://www.linkedin.com/in/williamglazercavanagh/}{linkedin.com/in/williamglazercavanagh}
    $|$ \textbf{GitHub}: \href{https://github.com/williamGlazer}{github.com/williamGlazer}
    $|$ \textbf{Website}: \href{https://williamglazer.github.io}{williamglazer.github.io}
  }
  \vspace{-12pt}
\end{itemize}


% 3. SKILLS
\section{Skills}
\vspace{-6pt}
\begin{itemize}[leftmargin=0.15in, label={}, itemsep=-3pt]
  \resumeItem{\textbf{Modeling}: PyTorch $|$ JAX $|$ Transformers (BERT/ESM) $|$ Object Detection $|$ RAG $|$ Fine-tuning}
  \resumeItem{\textbf{Infrastructure}: Docker $|$ Modal (Serverless) $|$ Dask $|$ Parquet/Zarr $|$ Distributed Systems}
  \resumeItem{\textbf{Core Stack}: Python $|$ SQL $|$ Bash $|$ ML System Design $|$ A/B Testing $|$ GPU Profiling}
\end{itemize}

\vspace{-12pt}

% 4. EXPERIENCE
% split by projects - brief description + role
% should I mention hired intern => I => II
% Problem => Accomplished X, as measured by Y, by doing Z
\section{Work Experience}
\resumeSubHeadingList
\resumeSubheading
{AbCellera}{Montreal/Vancouver}{Machine Learning Scientist II}{05/2023 - Current}

% description: protein engineering
\resumeItem{\textbf{Project: ML for Protein Engineering} (Risk Assessment \& Inference)}
\resumeSubHeadingList
% intent: performance engineering
\resumeItem{\textbullet\ \textbf{Accelerated Transformer inference by 30x:} Removed serial bottlenecks and vectorized pre-processing to saturate GPUs for multiple Foundation Models.}
% intent: distributed systems
\resumeItem{\textbullet\ \textbf{Optimized distributed systems:} Reduced container startup latency by 90\% by using volume caching to enable linear scaling during serverless fan-out.}
% intent: fast learner 
\resumeItem{\textbullet\ \textbf{Translated complex science into working software:} Learned the biology domain to bridge Machine Learning, engineering, and research. Converted open-ended goals from Principal Scientists into clear engineering plans.}
% intent: ownership 
\resumeItem{\textbullet\ \textbf{Shipped risk assessment product:} Led the full product lifecycle from prototype to production. Enabled users to filter high-risk sequences, reducing downstream failure rates by 30\%.}
% intent: ML Systems 
\resumeItem{\textbullet\ \textbf{Engineered risk calibration system:} Validated custom data normalization strategies on noisy biological data with ablation studies. Applied this pipeline to calibrate Foundation Model probabilities, ensuring confidence scores aligned with empirical failure rates.}
\resumeSubHeadingListEnd

% computer vision
\textbf{Project: High-Throughput Computer Vision} (100k+ images/day)
\resumeSubHeadingList
% Efficient ML architecture design
\resumeItem{\textbullet\ \textbf{Maximized imaging throughput (400 to 1200 images/s):} Designed a lightweight architecture (MobileNet backbone + detection head) to replace heavy legacy models, hitting the imaging hardware's physical limits.}
% ML Systems
\resumeItem{\textbullet\ \textbf{Doubled performance on edge cases (0.4 to 0.8 mAP):} Built a tool for experts to flag model failures. Used this feedback to fine-tune the model on hard examples, fixing errors on unseen data.}
% Focus on the ML
\resumeItem{\textbullet\ \textbf{Automated data labeling:} Built a semi-supervised pipeline to label complex multi-class assays. Validated quality with blind A/B tests, achieving an 80\% preference rate from human experts over the previous baseline.}
% performance engineering
\resumeItem{\textbullet\ \textbf{Eliminated Training Bottlenecks:} Engineered a sharded data format (separating metadata in Parquet from tensors in Zarr) for 1TB-scale microscopy data. Leveraged Dask for parallel processing to fully saturate GPU utilization during training..}
% thinking strategically TODO: poor lead in
\resumeItem{\textbullet\ \textbf{Saved weeks of engineering time:} Ran ablation studies on noisy data to demonstrate that simpler clustering architectures macthed Deep Learning performance, saving engineering time and reducing inference costs.}
\resumeSubHeadingListEnd

\resumeSubheading
{Croesus}{Montreal}{Research Intern}{05/2021 - 08/2021}
\resumeSubHeadingList
% RAG
\resumeItem{\textbullet\ \textbf{Evaluated Retrieval-Augmented Generation (RAG) feasibility:} Assessed early methods for injecting Knowledge Graphs into BERT-based architectures to define the research group's roadmap for grounding NLP models in factual data.}
\resumeSubHeadingListEnd

\resumeSubHeadingListEnd

\vspace{-12pt}

% 5. EDUCATION
\section{Education}
\resumeSubHeadingList

\resumeSubheading
{MSc. Machine Learning}{Professional Masters}{Graduation Year 2023}{University of Montreal (MILA)}
\resumeSubHeadingList
% RL JAX
\vspace{-4pt}
\resumeItem{\textbullet\ \textbf{Benchmarked JAX vs. PyTorch:} Re-implemented reinforcement leaning algorithms (TD3/VPG) using JAX (Haiku/Optax) to evaluate JIT compilation benefits. Accelerated training by 5x using XLA compilation compared to standard PyTorch (JIT Vs. Eager).}
\resumeSubHeadingListEnd

\resumeSubheading
{BEng. Software Engineering}{Artificial Intelligence Profile}{Graduation Year 2022}{Polytechnique Montreal}
\resumeSubHeadingList
\vspace{-4pt}
% research publication
\resumeItem{\textbullet\ \textbf{Published Research:} Co-authored \textit{Change Taxonomy for ML Pipelines} (Empirical Software Engineering, 2023).}
\resumeItem{\textbullet\ \textbf{Community Leadership:} Co-founded PolyAI, a student initiative for Applied AI.}
\resumeSubHeadingListEnd

\resumeSubHeadingListEnd

\end{document}